How the Practice of TDD Influences \\Class Design in Object-Oriented Systems: \\Patterns of Unit Tests Feedback

### 2013-01-31 sbes2012-english/paper.tex
ultimas modificacoes sugeridas pelo gerosa

%% ------------------------------------------------------------------------- %%
\section{Test-Driven Development}

@@

It is a known fact that class design tends to lose quality during the software evolution \cite{evolution-lehman}.
However, it is hard to discuss quality in terms of class design. In this study context,
we used the SOLID principles, detailed in Martin's work \cite{bob-martin}, which are
mentioned in the following section.

%% ------------------------------------------------------------------------- %%
\section{Quality of Class Design}

@@

%% ------------------------------------------------------------------------- %%
\section{Quantitative Analysis}

@@

%% ------------------------------------------------------------------------- %%
\section{Qualitative Analysis}

@@

%% ------------------------------------------------------------------------- %%
\section{Conclusion}
%\section{Conclusão}

>>>>

As a result of this study, we raised a few unit tests patterns, which gives developers
feedback on the quality of their class design. These patterns can be used by developers
to improve their class design cheaply.

This paper is divided as follows: in Section \ref{sec:tdd}, we discuss the principles
of Test-Driven Development; in Section \ref{cap:trabalhos-relacionados}, we present
some related work of this research; in Section \ref{sec:planejamento}, we describe the
study design; in Sections \ref{sec:quantitative} and \ref{sec:qualitative}, we present
our quantitative and qualitative results, respectively; in Section \ref{cap:ameacas},
we discuss the threats to validity of this research; in Section \ref{sec:conclusion},
we summarize the findings of this paper.

%% ------------------------------------------------------------------------- %%
\section{Test-Driven Development}
\label{sec:tdd}

@@

It is a known fact that class design tends to lose quality during the software evolution \cite{evolution-lehman}.
However, it is hard to discuss quality in terms of class design. In this study context,
we used the SOLID principles, detailed in Martin's work \cite{bob-martin}.

@@

%% ------------------------------------------------------------------------- %%
\section{Quantitative Analysis}
\label{sec:quantitative}

@@

%% ------------------------------------------------------------------------- %%
\section{Qualitative Analysis}
\label{sec:qualitative}

@@

%% ------------------------------------------------------------------------- %%
\section{Conclusion}
\label{sec:conclusion}
%\section{Conclusão}
